Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-15 paper/main.tex
Thoughts on the methods

>>>>

Thoughts on the general structure here: what it is (just based on headlines):

\begin{itemize}
  \item Detail on statistical model
  \item Detail on how annotation was done for AD
  \item Detail on how regressors were built for AD
  \item Detail on how annotation was done for AV
  \item Detail on how regressors were built for AV
  \item Detail on how regressors correlate
  \item How contrasts were built
\end{itemize}

\noindent what it could be:

Remind what the key question/story is (and what is it, actually?)

At the moment is think it is:

\begin{itemize}
  \item the PPA is not just a visual area
  \item it's presumed function can be mapped onto a natural stimulus (not just with an orthogonal task, but without any task)
  \item visual information is not necessary to observe differential activation congruent with PPA function in the PPA
\end{itemize}

a suitable method structure (for these aspects, and probably right after the stimulus description) could be:
\begin{itemize}
  \item What is the key strategy to address this question? (conduct "semantically analog" analyses on all three datasets, this could largely go to the end of the intro). Which specific cognitive processing to we contrast in AD vs AV
  \item Which ingredients to we need to make this happen? (take existing annotations, and define congruent contrasts based
    on regressors that are built from the respective annotations, available annotations could be described in a dedicated section in the methods)
  \item What do we need to check in order to ensure that subsequent analyses are valid? (is the necessary information in the natural stimuli uncorrelated enough? negative controls)
\end{itemize}
